TITLE OF YOUR PROJECT

### 2024-11-04 A3-Pt2.Rmd
load database

- John K. Samson (#########)
- John Darnielle (#########)
- Craig Finn (#########)
- Joel Plaskett (########)
- Ezra Furman (#########)

@@

It is recommended that you follow the structure of this template. The text is all placeholder - you are free to change any/all wording as you please, but it is very helpful for the grading process if you keep the same structure. Anything in <<double angle brackets>> definitely needs to be changed, but you are free to change any/all sentences!

@@

In this report, we are going to explore some aspects climate change and the impact and/or perceptions of it by using exploratory techniques. We'll explore <<general description of data>> using <<general description of techniques>>.

@@

## <<Data Set 1>>

```{r load_data1}
# Put in your code to load in the data set, along with any
# necessary cleaning beyond what was done in Part 1

# Note that the code in this document will not be shown
# when you click "knit", so the placement of this code
# chunk is purely for your benefit: You can see what happened
# with your data, which makes it easier to describe below!
```

The data come from <<place>> and describe <<more specific description of the data>>.

In order to clean the data, we <<steps to clean the data, concise but precise enough that a reader could follow your steps without seeing your code>>.

## <<Data Set 2>>

```{r load_data2}
# Put in your code to load in the data set, along with any
# necessary cleaning beyond what was done in Part 1

# Reminder: do NOT print your data to the screen unless it's
# completely necessary
```

The data come from <<place>> and detail <<more specific description of the data>>.

In order to clean the data, we <<steps to clean the data, concise but precise enough that a reader could follow your steps without seeing your code>>

## <<Data Set 3>>

```{r load_data2}
# Put in your code to load in the data set, along with any
# necessary cleaning beyond what was done in Part 1
```

The data come from <<place>> and detail <<more specific description of the data>>.

In order to clean the data, we <<steps to clean the data, concise but precise enough that a reader could follow your steps without seeing your code>>

@@

We explored many aspects of the data, but will demonstrate three. These are <<insight 1>>, <<insight 2>>, and <<insight3>>

@@

Overall, we found <<general ideas>>.

@@

The easiest way is to use Rmd's [footnote](https://bookdown.org/yihui/rmarkdown/markdown-syntax.html#inline-formatting) syntax. This will put a number beside the word where the footnote appears, and the full text of the footnote at the bottom of the page (pdf) or end of the document (html). The syntax is:^[See the source view to see this footnote], where I suggest that you put in something like this^[The relevance to the insight is ... . From <<name of source and name of article>>, published on <<date>>, url: <<link to page>>] to make references for this assignment.

>>>>

-   John K. Samson (\#########)
-   John Darnielle (\#########)
-   Craig Finn (\#########)
-   Joel Plaskett (\########)
-   Ezra Furman (\#########)

@@

It is recommended that you follow the structure of this template. The text is all placeholder - you are free to change any/all wording as you please, but it is very helpful for the grading process if you keep the same structure. Anything in \<<double angle brackets>\> definitely needs to be changed, but you are free to change any/all sentences!

@@

In this report, we are going to explore some aspects climate change and the impact and/or perceptions of it by using exploratory techniques. We'll explore \<<general description of data>\> using \<<general description of techniques>\>.

@@

## \<\<Data Set 1\>\>

```{r load_data1}
# Put in your code to load in the data set, along with any
# necessary cleaning beyond what was done in Part 1
cyclones_data <- read_parquet("cyclones_data.parquet")
cyclones_data
# Note that the code in this document will not be shown
# when you click "knit", so the placement of this code
# chunk is purely for your benefit: You can see what happened
# with your data, which makes it easier to describe below!
```

The data come from \<<place>\> and describe \<<more specific description of the data>\>.

In order to clean the data, we \<\<steps to clean the data, concise but precise enough that a reader could follow your steps without seeing your code\>\>.

## \<\<Data Set 2\>\>

```{r load_data2}
# Put in your code to load in the data set, along with any
# necessary cleaning beyond what was done in Part 1
ice_extent_yearly <- read_parquet("ice_extent_yearly.parquet")
ice_extent_yearly
# Reminder: do NOT print your data to the screen unless it's
# completely necessary
```

The data come from \<<place>\> and detail \<<more specific description of the data>\>.

In order to clean the data, we \<\<steps to clean the data, concise but precise enough that a reader could follow your steps without seeing your code\>\>

## \<\<Data Set 3\>\>

```{r load_data2}
# Put in your code to load in the data set, along with any
# necessary cleaning beyond what was done in Part 1
climate_awareness <- read_parquet("climate_awareness.parquet")
climate_awareness
```

The data come from \<<place>\> and detail \<<more specific description of the data>\>.

In order to clean the data, we \<\<steps to clean the data, concise but precise enough that a reader could follow your steps without seeing your code\>\>

@@

We explored many aspects of the data, but will demonstrate three. These are \<\<insight 1\>\>, \<\<insight 2\>\>, and \<<insight3>\>

@@

Overall, we found \<<general ideas>\>.

@@

The easiest way is to use Rmd's [footnote](https://bookdown.org/yihui/rmarkdown/markdown-syntax.html#inline-formatting) syntax. This will put a number beside the word where the footnote appears, and the full text of the footnote at the bottom of the page (pdf) or end of the document (html). The syntax is:[^1], where I suggest that you put in something like this[^2] to make references for this assignment.

[^1]: See the source view to see this footnote

[^2]: The relevance to the insight is ... . From \<<name of source and name of article>\>, published on \<<date>\>, url: \<<link to page>\>
